Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

% FIXME Talk about the bias of permutation FI in highly correlated settings
\noindent Estimating feature importance for highly-correlated datasets is a complicated task.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features.
Methods like \ac{PDP} do not produce reliable estimates in such scenarios because unrealistic situations between covariates are created \cite{molnar2019}.
% FIXME: Add ref
Due to the noisiness of the dataset, estimates from model-agnostic approaches such as permutation-based feature importance should also be taken with care.
This method calculates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the variance in the measure, reflecting the importance of the specific feature for the current model.
Permuting every feature $y$ times comes with some computational cost.
To balance the effort/gain ratio and cope with limited visual space in plots, we estimated the feature importance only for datasets HR and VI using the best performing learner of the benchmark.

>>>>

% FIXME Talk about the bias of permutation FI in highly correlated settings
\noindent Estimating feature importance for highly-correlated datasets is a complicated task.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features.
Methods like \ac{PDP} do not produce reliable estimates in such scenarios because unrealistic combinations between covariates are created \cite{molnar2019}.
% FIXME: Add ref
Due to the noisiness of the dataset, estimates from model-agnostic approaches such as permutation-based feature importance should also be taken with care.
This method calculates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the variance in the measure, reflecting the importance of the specific feature for the current model.
Permuting every feature $y$ times comes with some computational cost.
To balance the effort/gain ratio and cope with limited visual space in plots, we estimated the feature importance only for datasets HR and VI using the best performing learner of the benchmark.
